 %curriculum vitae   - for 2-years review
\newcommand{\comment}[1]{}

\newcommand{\ratio}[1]{{\tt Acceptance ratio: #1}}

\documentstyle[]{article}

\def\PHD{{*}}
\def\PHD{{}}

\setlength\topmargin{-0.29in}
\setlength{\textheight}{8.6in} % width of body
\setlength{\textwidth}{6.9in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
%\setlength{\topmargin}{-0.29in}
%\setlength{\textheight}{8.2in}
\setlength{\baselineskip}{1.3\baselineskip}
\setlength{\itemsep}{1.3\itemsep}
 \newcommand{\comm} [1]{}

 \input pankmac


 % removing the numbering of the 1st page
 %\gdef\thepage{}

 \begin{document} % End of preamble and beginning of text.




    \begin{center}
       {\bf\Large\bf Alon Efrat --- Curriculum Vitae }
    \end{center}

\vspace{4mm}
    \makebox{
    \parbox{2.6in}{\centering
    {\small
    Department of Computer Science\\
    University of Arizona\\
    Tucson, AZ 85721\\
    }
    }
    \nolinebreak
    \parbox{3.2in}{\centering
    {\small
    Email: {\tt alon@cs.arizona.edu}\\
    Phone: (520) 626-8047, Fax: (520) 621-4246 \\
    Web page: {\tt www.cs.arizona.edu/people/alon}
    }
    }}

    \vspace{8mm}


    \thispagestyle{empty}

    \comment{
   \noindent{\large\bf Research Interests}
    \begin{quote}
       I am interested in computational geometry, and in
       applications of geometric algorithms to real life problems.
       More specifically, my interests include geometric pattern matching,
       realistic input models, geographic information science, spatial data structures,
       and algorithms for mobile robots.
    \end{quote}
    }
    \comm{
   \noindent  {\bf Address:}
    Department of Computer Science \\
    Gould-Simpson Building \\
    1040 E 4th Street \\
    The University of Arizona \\
    PO BOX 210077 \\
    Tucson AZ 85721-0077\\
    }

    \vspace{5mm}
   \noindent{\large\bf Education}

    \vspace{3mm}

    \begin{tabular}{lll}


       1998 & Ph.D.\ Computer Science, Tel-Aviv University, Israel\\
       & Thesis: {\em Optimal Geometric Location Problems}\\
       & Advisor: Prof.\ Micha Sharir
       & \\

       1993 & M.Sc.\ Computer Science, The Technion, Israel \\
       & Thesis: {\em Maintaining the Smallest Enclosing Circle} \\
       & Advisors: Prof.\ Alon Itai and Prof.\ Reuven Bar-Yehuda \\


       1991 & B.Sc.\ Applied Mathematics,
       Mathematics Department, The Technion, Israel \\
       & \\

    \end{tabular}

\vspace{6mm}
   \noindent{\large\bf Professional Experience}

    \vspace{2mm}

    \begin{tabular}{lll}
       2000 - present& Assistant Professor, Computer Science Department, University of Arizona\\

       2000 - 2002& Visiting Researcher and Consultant, IBM Almaden Research Center\\

       1999 - 2000& Post Doctorate Research Fellow (Sponsor: Leonidas Guibas), Stanford University \\

       1994 - 1998& Instructor, Computer Science Department, Tel-Aviv University, The Technion, Israel
       & \\

    \end{tabular}

    \vspace{6mm}



{




 \noindent{\large\bf Awards and Grants }
  \begin{quote}
     \begin{tabular}{ll}


2005 & ACIST: Video Browsing with application  for KUAT programs.
With  Kobus Barnard. \$95,000 \\

2005 & NSF:  Databases for moving objects for  the {\em  Large Synoptic Survey
Telescope
(LSST)}. With \\
& Kobus Barnard and  Bongki Moon.
\$205,000. \\


2004 & NSF  REU Supplement: ITR/Collaborative Research: Intelligent Topology Control and
Energy  \\ & Provisioning for Wireless Video Sensor Networks. \$6,000 \\


2004 & NSF CAREER Grant 0348000.  Pattern Matching, Realistic Input Models and Sensor
Placement. \\& Useful Algorithms in Computational
Geometry. Duration 2004--2007. \$403,000 \\




2003 & NSF Grant 0312443 --- ITR/Collaborative Research: Intelligent Topology Control and
Energy \\ &  Provisioning for Wireless Video Sensor Networks. With Steve Pink (Co-PI) \\&
Duration is 2002-2005. \$122,126.


% 2002 &    {\bf Patents: }   Buddy Tracking --- A system for proximity alerts between
% friends. Currently in a filling stage.

\\

2002 & NSF Grant 0222920 --- Visualization of Giga-Graphs and Graph Processes. With
Stephen\\ & Kobourov  (PI)
and James Abelo. Duration is 2002-2005. \$240,000.                          \\


2002 & Honda Research Laboratory   (a gift with Joe Mitchell (co-PI)),   \$55,000 \\



          1998 & The Rothschild Fellowship, Israel (Post Doctorate Fellowship),  \$24,000. \\

          1998 & The Minerva Fellowship  Israel---Germany (Post Doctorate Fellowship)\\

          1998 & The Chateaubriand Fellowship,  French  (Post Doctorate Fellowship)\\

         % 1998 & The Pacific Institute for the Mathematical Sciences,
          %Canada,  (Post Doctorate Fellowship).  \\

          1996 & The Maus prize and grant for distinguished graduate students, Tel-Aviv University,
\$3000 \\
       \end{tabular}
%\vspace{2mm}

%{\bf Comment: } The NSF proposal,  ``Detecting and Exploiting Similarities between Code
%Sequences '' with Saumya Debray PI and
% John Kececioglu, was not granted, but out of 8 reviewers, 2 ranked it ``excellent'' and 4
% ranked it ``very good''.

    \end{quote}


%-------------------------
\newpage

\noindent{\large\bf Services to the community }
 \begin{quote}
    \begin{itemize}


\item   Conference local chair, the  22th\  ACM Symp.\ of Computational Geometry. To take
place in Sedona, June 2006.


%\item Co-organizer, with Gerald Farin. Workshop on ``Applications of Computational
%Geometry for Geometric Design'', to be held with the {\em SIAM Conf.\ on Geometric
%Design}, Phoenix 2005.



\item Program Committee member for the   21th.\ ACM  Symp.\ of Computational Geometry
2005.

%\item Open question Committee member for the  21th.\ ACM  Symp.\ of Computational
%Geometry 2005.

\item A guest editor of the special  issue of the {\em International Journal of
Computational Geometry and Applications (IJCGA)} dedicated to selected papers from the
21th.\ ACM  Symp.\ of Computational Geometry 2005.



\item NSF panel review,  2005.

%\item{\bf Refereeing reports}

 %\begin{description}

%\item[ Referee reports for journals: ] Discrete and Computational Geometry,
% Combinatorica, Information Processing Letters, Computational Geometry: Theory and Applications,
% International Journal of Computational Geometry and Applications,
% Journal of Algorithms,
% IEEE Transactions on Pattern Analysis and Machine Intelligence,
%  IEEE Transactions on Robotics and Automation,
%  IIE Transactions: Operations Engineering.




%\item[ Referee reports for conferences: ]
% Annual ACM-SIAM Symposium on Discrete Algorithms,
% IEEE Symposium on Foundations of Computer Science, ACM Annual Symposium on Computational Geometry.
%Workshop on Fundation of Robotics.
%\end{description}
\end{itemize}
\end{quote}

%----------------------
%\newpage
%    \begin{center}
%       {\Large\bf List of Publications}
%    \end{center}

\vspace{5mm}


\noindent{\large\bf  Students and Post-Doctorate Researchers    }

\begin{quote} \vspace{2mm}
\begin{description}

\item[Cesim Erten,] Post-Doctorate research assistant. 2004--current.

\item[Carola Wenk,] Post-Doctorate research assistant.  2000-2001. Currently a
faculty at the Computer Science Department at the University of Texas at
San-Antonio.

\item[Lingesh  Palaniappan,] Master student (2001-2003).  Currently at
Microsoft. Had an INFOCOM paper and an ICRA paper.

\vspace{5mm}


\end{description}

In addition, worked with other PhD students: Jesus Arango,  Quanfu Fan and
recently Justin  Cappos (all at the University of Arizona).

\end{quote}


\vspace{15mm}




 \noindent{\large\bf  List of Publications}

\vspace{2mm}


    %=============================================
\noindent
{\bf A. Patents }
\begin{enumerate}
\smallskip
\item
Buddy Tracking --- A system for proximity alerts between friends. US  2004/0198398.

\end{enumerate}


    %=============================================
\noindent{\bf B. Papers in Journals}
    % \smallskip

\begin{enumerate}


\item        \PHD
 P.K. Agarwal, A. Efrat, M. Sharir and S. Toledo,
 Computing a segment-center for a planar point set,
 {\it J. Algorithms} 15 (1993), 314--323.
 \vspace{1mm}




\item         \PHD
 A. Efrat, M. Sharir and G. Rote,
 On the union of fat wedges and separating a collection
 of segments by a line,
 \cgta\ 3 (1994), 277--288.
 \vspace{1mm}

\item          \PHD
 A. Efrat and C. Gotsman,
 Subpixel image registration using circular fiducials,
 \ijcga\ 4 (1994), 403--422.
 \vspace{1mm}

\item           \PHD
 A. Efrat, M. Sharir and A. Ziv,
 Computing the smallest $k$-enclosing circle and related problems.
 \cgta\ 4 (1995), 119--136.
 \vspace{1mm}



\item            \PHD
 A. Efrat and M. Sharir,
 A near-linear algorithm for the planar segment center problem,
 \dcg\ 16 (1996), 239--257.
 \vspace{1mm}


\item              \PHD
 A. Efrat and O. Schwarzkopf,
 Separating and shattering long line segments.
 \ipl\ 64 (1998), 309--314.
 \vspace{1mm}



\item               \PHD
 L.P. Chew, D. Dor, A. Efrat and K. Kedem,
 Geometric pattern matching in $d$-dimensional space,
 \dcg\ 21 (1999) 257--274.
 \vspace{1mm}



\item       \PHD
 A. Efrat and M.J. Katz,
 On the union of $\kappa$-curved objects,
 \cgta\ 14 (1999), 241--254.
 \vspace{1mm}


\item       \PHD
 A. Efrat and M. Sharir,
 On the complexity of the union of fat objects in the plane,
\dcg\  23 (2000), 171--189.
 \vspace{1mm}

\item             \PHD
 P.K. Agarwal, A. Efrat and M. Sharir,
 Vertical decomposition of shallow levels in 3-dimensional
 arrangements and its applications,
 \soc\ 29 (2000), 912--953.
 \vspace{1mm}



\item        \PHD
 A. Efrat, M.J. Katz, F. Nielsen and M. Sharir,
 Dynamic data structures for fat objects and their applications.
 \cgta\
15 (2000), 215-227.



\item         \PHD
 A. Efrat and M.J. Katz,
 Computing an Euclidean bottleneck matching in higher dimension.
 \ipl.  4 (2000), 169--174.



\item      \PHD
 A. Efrat, M.J. Katz and A. Itai,
 Geometry helps in bottleneck matching and related problems,
 \algc \ 1 (2001) 1--28.
 \vspace{1mm}


\item
 A. Amir, A. Efrat, P. Indyk and H. Samet,
 Efficient algorithms and regular data structures for dilation,
 location and proximity problems. \algc\ (2001) 166--187.
 \vspace{1mm}




\item       \PHD
 B. Aronov, A. Efrat, D. Halperin and M. Sharir,
 A subquadratic bound on the number of regular vertices
 of the union of Jordan regions.
 \dcg\  25 (2001), 203--220.
 \vspace{1mm}


\item           \PHD
 T. Chan  and A.\ Efrat
 Fly Cheaply: On the Minimum Fuel-Consumption Problem.
 \jalg\ 41 (2001), 330--337.
 \vspace{1mm}

\item
Nigel Davis, Keith Cheverst, Keith Mitchell and Alon Efrat,
Using and Determining Location in a Context-Sensitive  Tour
Guide: The Guide Experience. {\em IEEE computers}  34 (2001), 35--41.
 \vspace{1mm}


\item A. Efrat, F. Hoffmann, K. Kriegel, C. Schultz and C. Wenk,
 geometric algorithms for the analysis of 2D-Electrophoresis gels.
{\em Journal of Computational Biology},  (special issue dedicated to RECOMB 2001), 9
(2002), 299--316.
 \vspace{1mm}


\item A. Efrat, L. J. Guibas, S. Har-Peled, J. S. B. Mitchell and  T.M. Murali. new
similarity measures between polylines with applications to morphing and polygon sweeping.
\dcg\  (2002),  535--569.
 \vspace{1mm}








\item A. Efrat, F.  Hoffmann,  K.  Kriegel,  C.  Knauer,  G.  Rote and C. Wenk, covering
shapes by ellipses {\em Algorithmica  (special issue on shape algorithms)}  (2003),
145--160.
 \vspace{1mm}


\item A. Amir and  S. Srinivasan, Search the Audio, Browse the Video --- a generic
paradigm for video collections. {\em EURASIP Journal on Applied Signal Processing,}
2(2003), 209--222.
 \vspace{1mm}


\item H. Alt, A. Efrat, G. Rote and C. Wenk.  matching planar maps, {\it  J. Alg.\ }, 49
(2003) 262--283.
 \vspace{1mm}


\item
 A.\ Efrat,
 The Complexity of the Union of $(\alpha,\beta)$-Covered Objects.
 \soc, 34(2005) 755--787.

 \vspace{1mm}

\item
 A. Efrat, P. Indyk and S. Venkatasubramanian.
 Pattern Matching for Sets of Segments. \algc, to appear.



 \vspace{1mm}

\item A. Efrat, S. Kobourov and  A. Lubiw, Computing Homotopic Shortest Paths
Efficiently. \cgta\ to appear.

 \vspace{1mm}

\item B.\  Aronov, A.\  Efrat, V.\  Koltun and M.\  Sharir, On the Union of
$\kappa$-Round Objects in Three and Four Dimensions, \dcg \  (special issue dedicated to
\scg{20}). To appear.


\item
 P. Brass, E. Cenek, C. A. Duncan,
 A. Efrat, C. Erten, D. Ismailescu,
 S. G. Kobourov, A. Lubiw and J. S. B. Mitchell, On Simultaneous,
 Planar Graph Embeddings, \cgta, to appear.
 \vspace{1mm}



\item A.\ Efrat, L.J. Guibas and O.A.\ Hall-Holt and L. \ Zhang,
 On Incremental Rendering of Silhouette Maps of a Polyhedral Scene.
\cgta\ to appear.
 \vspace{1mm}

\item  O.  Cheong, A.  Efrat and S.  Har-Peled,
 On Finding a Guard that Sees Most and a Shop that Sells Most,
 \dcg\ to appear.

\item  A. Efrat, C. Erten and S. Kobourov. Fixed-Location Circular Arc Drawings
{\em Journal of Graph Algorithms and Applications}. To Appear.



\item A. Efrat and S. Har-Peled, Locating Guards in Art Galleries, {\em
Information Processing Letters}, to appear.




 \item
 C. A. Duncan, A. Efrat, S. G. Kobourov and  C. Wenk,
 Drawing with Fat Edges,  {\em International Journal of
Foundations of Computer Science (IJFCS) Special Issue of  on Graph Drawing.} To
appear.





\item A. Amir, A. Efrat, J.  Myllymaki,  L. Palaniappan  and K. Wampler, Buddy
tracking
--- efficient proximity detection  among mobile friends, {\em Pervasive and Mobile
Computing}, to appear after revision.
 \vspace{1mm}


\item  A.\ Efrat, Q.\  Fan and S.\  Venkatasubramanian,
     Curve Matching, Time Warping, and Light Fields,  New Algorithms for
Computing Similarity between Curves, {\em J.\ Mathematic Imaging and Vision},
to appear after revision.

\item  Y.T. Hou, Y. Shi, J. Pan, A. Efrat, and S.F. Midkiff, "Maximizing
lifetime of wireless sensor networks through optimal single-session flow
routing,"  in {\em IEEE Transactions on Mobile Computing}, to appear.

 \vspace{1mm}



  %Y. Shi, Y.T. Hou, and A. Efrat, "Design of low-complexity approximation algorithms for base station
  % placement problems in sensor networks," Technical Report,
  %The Bradley Dept. of ECE, Virginia Tech, July 2005
 \vspace{1mm}
\end{enumerate}
%================================

\vspace{15mm}

 %\newpage
\noindent
{\bf C. Papers in Proceedings of Peer-Reviewed   Conferences}

\begin{enumerate}
 %\smallskip




\item      \PHD
 A. Efrat, M. Sharir and A. Ziv,
 computing the smallest $k$-enclosing circle and related problems.
 {\em Proc.\ Third Workshop Algorithms Data Struct.\ (WADS) }
 {\em LNCS\/} 1993,
 vol.\ 709,
 325--336.
 \vspace{1mm}


\item          \PHD
 A. Efrat and C. Gotsman,
 subpixel image registration using circular fiducials,
{\em Proc.\ of the second  Israeli Symposium on Theory of Computing and Systems} 1994,  127--136.
 \vspace{1mm}

\item        \PHD
 A. Efrat and M. Sharir,
 near-linear algorithm for the planar segment center problem, \soda{5}
 1994, 87--97.
 \vspace{1mm}

\item            \PHD
 P.K. Agarwal, A. Efrat and M. Sharir,
 vertical decomposition of shallow levels in 3-dimensional
 arrangements and its applications,
 \scg{11}, 1995, 39--50.
 \vspace{1mm}

\item               \PHD
 L.P. Chew, D. Dor, A. Efrat and K. Kedem,
 geometric pattern matching in $d$-dimensional space,
 {\em 3rd European Symposium on Algorithms (ESA)},
 {\em LNCS \/}
 vol.\ 979,   1995,  264--279.
 \vspace{1mm}



\item                \PHD
 A. Efrat and A. Itai,
 improvements on bottleneck matching
 and related problems, using geometry.
 \scg{12}, 1996, 301--310.
 \vspace{1mm}



\item                  \PHD
 A. Efrat and M.J. Katz,
 computing most-uniform and minimum deviation matchings
 in geometric settings.
 {\em Proc.\ 7th Annual
 International Symposium on Algorithms and Computational (ISAAC)},
 1996, 115--125.
 \vspace{1mm}



\item                 \PHD
 A. Efrat and O. Schwarzkopf,
 separating and shattering long line segments,
{\em  Proc.\ 7th Annual
 International Symposium on Algorithms and Computational (ISAAC)},
 1996, 36--44.
 \vspace{1mm}


\item                  \PHD
 A. Efrat and M. Sharir,
 on the complexity of the union of fat objects in the plane,
 \scg{13}, 1997, 104--112.
 \vspace{1mm}

\item                   \PHD
 A.\ Efrat, M.J.\ Katz, F.\ Nielsen and M.\ Sharir,
 dynamic data structures for fat objects and their applications.
 {\em Proc.\ 5th Workshop on Algorithms and Data Structures},
 1997,
 297--396.
 \vspace{1mm}



\item                     \PHD
 A.\ Efrat and M.J.\ Katz,
 on the Union of $\alpha$-curved Objects,
 \scg{14}, 1998, 206--213.
 \vspace{1mm}

\item                       \PHD
 A.\ Efrat and S.\ Har-Peled,
 fly Cheaply: on the Minimum fuel-consumption problem,
 \scg{14}, 1998, 143--145.
 \vspace{1mm}



\item                         \PHD
 B.\ Aronov, A.\ Efrat, D.\ Halperin and M.\ Sharir,
 a subquadratic bound on the number of regular vertices
 of the union of Jordan regions.
 \swat{6}, 1998, 322--334.
 \vspace{1mm}


\item
 A.\ Efrat,
 The Complexity of the Union of $(\alpha,\beta)$-Covered Objects,
 \scg{15}, 1999, 134--142.
 \vspace{1mm}


\item
 A.\ Amir, A.\ Efrat, P.\ Indyk and H.\ Samet,
 efficient algorithms and regular data structures for dilation,
 location and proximity problems, \focs{40}, 1999, 160--170.
 \vspace{1mm}

 %Pankaj: what to do with J.C.

\item
 H. H.\ Gonzalez-Banos, E. Mao, J.C. Latombe,
 T. M. Murali and A.\ Efrat,.
 Planning Robot Motion Strategies for Efficient
 Model Construction, {\em Proc.\ 9th International Symposium of Robotics Research}, 2000,
 345-352.
 \vspace{1mm}

\item A.\ Efrat, L.J. Guibas,  O.A.\ Hall-Holt and L. \ Zhang,
 On Incremental Rendering of Silhouette Maps of a Polyhedral Scene.
 \soda{11}, 2000, 910--917.
 \vspace{1mm}




\item
 A.\ Efrat,  L.J.\ Guibas,  S.\ Har-Peled,  D.C. Lin,  J.S.B. Mitchell,
 T.M.\ Murali.
 sweeping simple polygons with a chain of guards.
 \soda{11}, 2000. 297--936.
 \vspace{1mm}




\item
 A. Efrat, P. Indyk and S. Venkatasubramanian.
 pattern matching for sets of segments. \soda{12}, 2001, 295--304.

 \vspace{1mm}



\item
 A. Efrat, S. Har-Peled, L. Guibas and T.M. Murali,
 morphing between Curves. \soda{12}, 2001, 680--689.
 \vspace{1mm}




\item Alon Efrat, Frank Hoffmann, Klaus Kriegel, Christof Schultz and
 Carola Wenk.
 geometric algorithms for the analysis of 2D-Electrophoresis gels,
 {\em The Fifth Annual International Conference on
 Computational Molecular Biology (RECOMB)}, 2001,  114-123. %ratio 35/128
 \vspace{1mm}


 \item
 C. A. Duncan, A. Efrat, S. G. Kobourov and  C. Wenk,
 Drawing with Fat Edges,  {\em Graph Drawing (GD)}  2001. LNCS vol.\  2265,  162--177.
 \vspace{1mm}



\item A. Amir, A. Efrat and S. Srinivasan,
 developments in phonetic word retrieval, {\em
 ACM Tenth International Conference on Information
and Knowledge Management (CIKM) 2001} ,  580--582.
 \vspace{1mm}



\item A. Efrat, F.  Hoffmann,  K.  Kriegel,  C.  Knauer,  G.  Rote and C. Wenk, Covering
Shapes by Ellipses \soda{13}, 2002, 453--454.
 \vspace{1mm}



\item
A. Efrat and S. Har-Peled, Locating Guards in Art Galleries,
{\em 2nd IFIP International Conference on
Theoretical Computer Science }  2002, 181--192.
 \vspace{1mm}


\item A. Efrat, S. Kobourov and  A. Lubiw, Computing Homotopic Shortest Paths
Efficiently, {\em European Symposium on Algorithms (ESA)} 2002, 411--423.
 \vspace{1mm}




\item H. Alt, A. Efrat, G. Rote and C. Wenk,  Matching Planar Maps, \soda{14} 2003,
589--592.
 \vspace{1mm}



\item A. Efrat,  H. H. Gonz\'alez-Banos,  S. Kobourov and L. Palaniappan, Optimal Motion
Strategies to Track and Capture a Predictable Target, {\em  IEEE  International
Conference on Robotics and Automation}, 2003.
 \vspace{1mm}


\item M. Dror, A. Efrat,  A. Lubiw  and  J. S. B. Mitchell, Touring a Sequence of
Polygons, {\em ACM Symposium on Theory of Computing (STOC)} 2003, 473--482.
 \vspace{1mm}



\item
 P. Brass, E. Cenek, C. A. Duncan,
 A. Efrat, C. Erten, D. Ismailescu,
 S. G. Kobourov, A. Lubiw and J. S. B. Mitchell, On Simultaneous,
 Planar Graph Embeddings, {\em Workshop on Data Structures (WADS)
  } 2003,  243--255.
 \vspace{1mm}




\item A.  Efrat, C.  Erten and S.  Kobourov Fixed-Location Circular-Arc Drawing  of
Planar Graphs, {\em Graph Drawing (GD) 2003}  147--158.
 \vspace{1mm}


\item
O.  Cheong, A.  Efrat and S.  Har-Peled,
 On Finding a Guard that Sees Most and a Shop that Sells Most,
 {\it  ACM-SIAM Symposium on Discrete Algorithms}, 2004, 1098--1107.
 \vspace{1mm}


\item A. Amir, A. Efrat, J.  Myllymaki,  L. Palaniappan  and K. Wampler, Buddy tracking
--- efficient proximity detection  among mobile friends {\em\  The 23rd Conference of the
IEEE Communications Society (INFOCOM)} 2004.
 \vspace{1mm}


\item
 J.\  Arango, M.\  Degermark, A.\  Efrat and  S.\  Pink, an efficient flooding algorithm for mobile Ad-hoc networks,
{\em Modeling and Optimization in Mobile, Ad Hoc and Wireless Networks (WiOpt)},  2004.
 \vspace{1mm}




\item B.\  Aronov, A.\  Efrat, V.\  Koltun and M.\  Sharir, On the Union of
$\kappa$-Round Objects in Three and Four Dimensions, \scg{20} (2004), 383--390.
 \vspace{1mm}

\item Q.\ Fan,  A.\ Efrat,  V.\  Koltun,  S.\  Krishnan and S.\  Venkatasubramanian,
 Hardware-Assisted Natural Neighbor Interpolation. {\em Workshop on Algorithm
Engineering and Experiments (ALENEX05)} 2005. \ratio{15/61}.


\item  A.\ Efrat,    S.\ Har-Peled and J.\ Mitchell.  Approximation Algorithms
for Two Optimal Location Problems in Sensor Networks.  {\em BroadNets  IEEE 2nd
Int.\ conf. on Broadband Communication, Networks and systems. (BROADNET)} 2005.

\item A. Iyer, A.\ Efrat,  C.\ Erten, D.\ Forrester and   S.\ Kobourov,
Force-Directed Approaches to Sensor Localization, {\em Workshop on Algorithm
Engineering and Experiments (ALENEX)} 2006.


\item E.\  Ezra and M.\ Sharir and A.\  Efrat, On the ICP Algorithm, {\em  ACM
Symposium on Computational Geometry (SoCG), 2006}, to appear.



\end{enumerate}

\vspace{25mm}

 %\newpage
\noindent {\bf C. Papers in Non-Competitive Venues. }

\begin{enumerate}



\item   \PHD
 R. Bar-Yehuda, A. Efrat and A. Itai,
 A simple algorithm for maintaining the center of a planar point-set,
 {{\it Proc.\ 5th Canad.\ Conf.\ Comput.\ Geom.\/}}
 1993, 252--257.
 \vspace{1mm}

\item    \PHD
 A. Efrat, M. Lindenbaum and M. Sharir,
 finding maximally consistent sets of halfspaces,
 {{\it Proc.\ 5th Canad.\ Conf.\ Comput.\ Geom.\/}},
 1993, 432--436.
 \vspace{1mm}



\item     \PHD
 A. Efrat, M. Sharir and G. Rote,
 on the union of fat wedges and separating a collection of
 segments by a line,
 {{\it Proc.\ 5th Canad.\ Conf.\ Comput.\ Geom.\/}},
 1993, 115--120.
 \vspace{1mm}



\item  A. Efrat, S. G. Kobourov, M. Stepp, and C. Wenk, Growing Fat Graphs,
video contribution, \scg{18},  277--278, 2002.



\item  C. Wenk, H.  Alt, A.  Efrat, L. Palaniappan and  Günter Rote,  Finding a
curve in a map, video contribution, \scg{19}  384--385, 2003.



\item
 K. Barnard, A. Connolly, L. Denneau, A. Efrat, J. N. Heasley, R. Jedicke,
J. M. Kubica, B. Moon, A. Moore, S. Morris, P. Rao, The LSST moving object
pipeline, {\em Observatory operations: strategies, processes, and systems,
proceedings of SPIE} Vol. \#6270, 2006 (to appear).


\item
 J. Kubica, T. Axelrod, K. Barnard, A. Connolly, L. Denneau, A. Efrat, J.
Heasley, R. Jedicke, B. Moon, A. Moore, S. Morris, P. Rao, "Efficiently
Tracking Moving Sources in the LSST",  {\em The 207th meeting of the American
Astronomical Association.}





\end{enumerate}




\noindent
%{\bf C. Reports}
% \smallskip




%\item
% N. Cohen, A.\ Efrat and F. Bruckstein,
% On ants crickets and frogs in circular pursuit.
% Report. CIS-9309. {\em Faculty of Computer Science, Technion - IIT}.



%\item
% A.\ Efrat,
% Finding approximate matching of points and segments under translation,
% manuscript 1995.


%\end{enumerate}

% \noindent
% {\bf D. In Preparation}

% \begin{enumerate}

% \item
% A. Efrat,  H.  Gonz\'alez-Banos, S. Har-Peled and J. C.  Latombe,
% A Randomized Art-Gallery Algorithm for Sensor Placement.





% \item
% A. Amir,
% A.  Efrat, J.  Myllymaki, L.  Palaniappan and  K.  Wampler,
% Buddy tracking  --- efficient proximity detection  among mobile friends.



% \end{enumerate}



\comment{

 \noindent {\bf Other current     research areas: }
\begin{itemize}
% \item  Currently started collaborating with a start-up
% that  develops   technology for  enhancing the use of  ultrasound in cancer curing.

 \item  Initial contacts with a Astronomy researchers from NOAO
 about different geometric algorithms for manipulating data obtained from telescopes,
 and   controlling the motion of the telescopes.


 \item
 Working with Joe Mitchell (AMS, Stony Brook) and Hector  Gonz\'alez-Banos (Honda research lab)
 about different problems related to optimal sensor placement. An example of such a problem
 is how to locate cameras in airport terminals to be able to track suspicious people,
 while the choice of the locations of the cameras should take into account resources
 such as the cameras themselves, wiring, hardware allocated for the control etc.

 \item
 Continue the work with Carola Wenk on other about optimal algorithms for
 discovering proteins in electrophoresis gels. Several previous publications in this area
  are listed above.


\item Collaboration with Thomas Hou (Virginia Tech) about location problems in ad-hoc
sensors networks.


\end{itemize}


%\smallskip
%\begin{enumerate}

\newpage


\noindent{\large\bf Services to the community }
 \begin{quote}
    \begin{itemize}

\item NSF panel review, {\em CAREER award}, 2004.

\item Program Committee member for the {\em  21th.\ ACM  Symp.\ of Computational Geometry
2005}.

\item Open question Committee member for the {\em  21th.\ ACM  Symp.\ of Computational Geometry
2005}.

\item A guest editor of the special  issue of the {\em International Journal of
Computational Geometry and Applications (IJCGA)} dedicated to selected papers from the
{\em 21th.\ ACM  Symp.\ of Computational Geometry 2005}.


\item   Conference local chair, the  { \em 22th.\  ACM Symp.\ of Computational Geometry
2006} that  which will take place in Sedona in June 2006.



\item{\bf Refereeing reports}

 \begin{description}

\item[ Referee reports for journals: ] Discrete and Computational Geometry,
 Combinatorica, Information Processing Letters, Computational Geometry: Theory and Applications,
 International Journal of Computational Geometry and Applications,
 Journal of Algorithms,
 IEEE Transactions on Pattern Analysis and Machine Intelligence,
  IEEE Transactions on Robotics and Automation,
  IIE Transactions: Operations Engineering.




\item[ Referee reports for conferences: ]
 Annual ACM-SIAM Symposium on Discrete Algorithms,
 IEEE Symposium on Foundations of Computer Science, ACM Annual Symposium on Computational Geometry.
Workshop on Fundation of Robotics.
\end{description}
\end{itemize}
\end{quote}
%\newpage

\vspace{7mm }


}

\vspace{7mm }


\newpage

 \noindent{\large\bf Invited Presentations }

\vspace{3mm}

\begin{itemize}
\item Dagstuhl workshop on    Computational Geometry (1999).

\item Dagstuhl workshop on Computational Cartography (1999). Subject of the talk:
 Dilation and fast point location on Quad Trees.



\item Nacholim Workshop on Computational Geometry (1999). Subject of talk:
Sweeping a polygon with a chain of guards.






\item Computer Science Department, FU Berlin (1999).  Subject of talk:
Bottleneck Pattern Matching


\item American Mathematical Society Meeting at South Carolina (2000). Subject of talk:
Morphing between curves.

\item Dagstuhl workshop on    Computational Geometry (2001).


\item Honda Research labs (2002). Subject of the talk:
Art Gallery Problems.

\item Dagstuhl workshop on Computational Geometry (2003). Subject of talk:
Touring a Sequence of Polygons.



\item Seminars in other universities: Tel-Aviv University,  Ben-Gurion University, Texas
A\&M,  ECE department at the University of Arizona, and more.

\item Invited visit and talk in Caltech  (2005). Subject of talk: Sensors locations
problems.



\item Invited visit and talk in ASU (2005). Subject of talk: Sensors locations problems.



%\item Dagstuhl workshop on Graph Drawing (2005). TBD.

\item Dagstuhl workshop on Computational Geometry (2005) Subject of talk: On Sensor
Location Problems.


 \end{itemize}

\newpage

%=======================================


\comment{



 \noindent{\large\bf Submitted Presentations since 1997}

\vspace{3mm}

\begin{itemize}

\item
 A. Efrat and M. Sharir,
 On the complexity of the union of fat objects in the plane,
 \scg{13}, 1997.
 \vspace{1mm}




\item
 A.\ Efrat and M.J.\ Katz,
 On the Union of $\alpha$-Curved Objects,
 \scg{14}, 1998.
 \vspace{1mm}

\item
 A.\ Efrat and S.\ Har-Peled,
 Fly Cheaply: On the Minimum Fuel-Consumption Problem,
 \scg{14}, 1998.
 \vspace{1mm}



\item
 B.\ Aronov, A.\ Efrat, D.\ Halperin and M.\ Sharir,
 A subquadratic bound on the number of regular vertices
 of the union of Jordan regions.
 \swat{6}, 1998.
 \vspace{1mm}


\item
 A.\ Efrat,
 The Complexity of the Union of $(\alpha,\beta)$-Covered Objects,
 \scg{15}, 1999.
 \vspace{1mm}


\item A.\ Efrat, L.J. Guibas and O.A.\ Hall-Holt and L. \ Zhang,
 On Incremental Rendering of Silhouette Maps of a Polyhedral Scene.
 \soda{11}, 2000.



\item
 A. Efrat, S. Har-Peled, L. Guibas and T.M. Murali.
 Morphing between Curves. \soda{12}, 2001.




\item A. Efrat and S. Har-Peled, locating guards in art galleries {\em 2nd IFIP
International Conference on Theoretical Computer Science }  2002.


\end{itemize}

}


\noindent{\large\bf Teaching Experience}

\vspace{3mm}

\def\az{{The University of Arizona}}

\begin{itemize}

\item Will teach a seminar on  Optimization problems in sensors and ad-hoc
networks. \az.

\item Taught a course on C and Unix, \az.


\item Taught a course on  Geometric Algorithms,  \az.



\item Taught a seminar  on Geometric Matching and Applications to Biology, \az.

\item Taught a course on Computer Graphics,  and a courses on Advance Computer
Graphics, \az.


\item Taught a course on   Foundations of Computing, and a courses on
Algorithms, (introduction and advance levels), \az.



\item
 Collaborate in instructing seminars in Computational Geometry
 Stanford University.

\item
 Instructor at
 a course on Data Structures --- for undergraduate students.
 I taught this course in Tel-Aviv University, as well
 as a few other places (Technion, College for Management, IBM Israel),
 where it was a part of a course of programming for
 students having background in other fields.

\item Taught  a course on Graph Algorithms, in the Academic College of Tel-Aviv, and at
the Technion.

\item Teaching assistant in an advanced  course in Data Structures, The Technion.

\item Taught  courses of different levels in C and Unix Programming, Tel-Aviv University.


\item Instructor at a course in Discrete Mathematics, Tel-Aviv University.

\item
 Instructor at
 a seminar in Random Algorithms in Computational Geometry, Tel-Aviv University).

\item Taught a seminar on Geographic Information Systems and Computational Geometry,
Tel-Aviv University.

\item Was a member of a team at the Open University (Israel)
 that prepared courses for distance learning. These courses
 include Advanced Algorithms, File Systems and Computational Geometry.


\end{itemize}







\end{document}
